### 2025-01-28 paper/icml25/first/sects/background.tex
clarify why we do not consider partial observability in the formalization

\subsection{Neural Networks}
A neural network is a function $f_{\theta}:\mathbb{R}^n\rightarrow\mathbb{R}^m$ parameterized by its weights $\theta$, which maps an input vector $x\in\mathbb{R}^n$ to an output vector $y\in\mathbb{R}^m$. 
The network parameters $\theta$ are optimized by minimizing the loss function $\mathcal{L}_\theta$, which quantifies the discrepancy between the network's predictions and the target outputs based on the training data.

@@

For simplicity, we formally treat only the case where the policies observe the full state, meaning that $\stateobs{i}$ is the identity function. However, in our experiments, we consider also scenarios where the full state is not available to the policies.

>>>>

\subsection{Neural Networks}
A neural network is a function $f_{\theta}:\mathbb{R}^n\rightarrow\mathbb{R}^m$ parameterized by its weights $\theta \in \mathbb{R}^w$, which maps an input vector $x\in\mathbb{R}^n$ to an output vector $y\in\mathbb{R}^m$. 
The network parameters $\theta$ are optimized by minimizing the loss function $\mathcal{L}_\theta$, which quantifies the discrepancy between the network's predictions and the target outputs based on the training data.

@@

For simplicity, we formally consider only the case where policies have access to the full state, meaning that $\stateobs{i}$ is the identity function. This allows us to focus on the fundamental aspects of our approach without the added complexity of partial observability. Extending our framework to handle partial observability is straightforward; however, we choose not to address it here to maintain clarity and simplicity in our presentation. Nonetheless, our experiments do include scenarios where policies do not have access to the complete state information.
